---
output:
  pdf_document: default
  html_document: default
params:
    data: "."
    cregion: "cregion_table.tab"
---

```{r, message=FALSE, echo=FALSE, results="hide"}
# Setup
library(prestor)
library(knitr)
library(captioner)
if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("cprimers_count", "Count of assigned internal C-regions. 
                           The bar height indicates the total reads assigned to 
                           the given C-region, stacked for those under the error 
                           rate threshold (Pass) and over the threshold (Fail).")
figures("cprimers_hist", "Distribution of internal C-region match error rates. 
                          The error rate is the percentage of mismatches between the 
                          C-region sequence and the read for the best 
                          matching C-region. The dotted line indicates the error
                          threshold used.")
figures("cprimers_error", "Distribution of internal C-region match error rates, 
                           broken down by assigned C-region. The error rate
                           is the percentage of mismatches between the 
                           C-region sequence and the read for the best 
                           matching C-region. The dotted line indicates the error
                           threshold used.")
```

```{r, echo=FALSE}
cregion_log <- loadLogTable(file.path(params$data, params$cregion))
```

# Internal Constant Region Identification

The MaskPrimers tool is often used to identify constant region primers
used for isotype assignment. However, primer use is not always consistent
with the true constant region. To correct for this, a second iteration
of MaskPrimers is run to assign isotypes. The sequence set used as 
"primers" is the constant and terminal J consensus sequence expected to be
between the primer and bulk of the J region.

## Count of constant region matches

```{r, echo=FALSE}
plotMaskPrimers(cregion_log, titles=c("Assembled C-Region"), 
                style="count", max_error=0.3, sizing="figure")
```

`r figures("cprimers_count")`

## Constant region match error rates

```{r, echo=FALSE}
plotMaskPrimers(cregion_log, titles=c("Assembled C-Region"), 
                style="hist", max_error=0.3, sizing="figure")
```

`r figures("cprimers_hist")`

```{r, echo=FALSE}
plotMaskPrimers(cregion_log, titles=c("Assembled C-Region"), 
                style="error", max_error=0.3, sizing="figure")
```

`r figures("cprimers_error")`
