---
output:
  pdf_document: default
  html_document: default
params:
    data: "."
    consensus_1: "consensus-1_table.tab"
    consensus_2: "consensus-2_table.tab"
    consensus_titles: ["Read 1", "Read 2"]
---

```{R, message=FALSE, echo=FALSE, results="hide"}
# Setup
library(prestor)
library(knitr)
library(captioner)

plot_titles <- params$consensus_titles
if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("cons_size", 
        paste("Histogram of UMI read group sizes (reads per UMI) for",  
              plot_titles[1], "(top) and", plot_titles[2], "(bottom).",
              "The x-axis indicates the number of reads in a UMI group and the y-axis is the 
               number of UMI groups with that size. The Consensus and Total bars are overlayed 
               (not stacked) histograms indicating whether the distribution has been calculated 
               using the total number of reads (Total) or only those reads used for consensus 
               generation (Consensus)."))
figures("cons_prfreq", 
        paste("Histograms showing the distribution of majority primer frequency for all UMI read groups for",
              plot_titles[1], "(top) and", plot_titles[2], "(bottom)."))
figures("cons_prsize", 
        paste("Violin plots showing the distribution of UMI read group sizes by majority primer for",
              plot_titles[1], "(top) and", plot_titles[2], "(bottom).",
              "Only groups with majority primer frequency over the PRFREQ threshold set when running
               BuildConsensus. Meaning, only retained UMI groups."))
figures("cons_error", 
        paste("Histogram showing the distribution of UMI read group error rates for",
              plot_titles[1], "(top) and", plot_titles[2], "(bottom)."))
figures("cons_prerror", 
        paste("Violin plots showing the distribution of UMI read group error rates by majority primer for",
              plot_titles[1], "(top) and", plot_titles[2], "(bottom).",
              "Only groups with majority primer frequency over the PRFREQ threshold set when 
               running BuildConsensus. Meaning, only retained UMI groups."))
```

```{r, echo=FALSE}
consensus_log_1 <- loadLogTable(file.path(params$data, params$consensus_1))
consensus_log_2 <- loadLogTable(file.path(params$data, params$consensus_2))
```

# Generation of UMI Consensus Sequences

Reads sharing the same UMI are collapsed into a single consensus sequence by
the BuildConsensus tool. BuildConsensus considers several factors in determining
the final consensus sequence, including the number of reads in a UMI group, 
Phred quality scores (`Q`), primer annotations, and the number of mismatches 
within a UMI group. Quality scores are used to resolve conflicting base calls in
a UMI read group and the final consensus sequence is assigned consensus quality 
scores derived from the individual base quality scores. The numbers of reads in a UMI
group, number of matching primer annotations, and error rate (average base mismatches from 
consensus) are used as strict cut-offs for exclusion of erroneous UMI read groups.
Additionally, individual reads are excluded whose primer annotation differs from 
the majority in cases where there are sufficient number of reads exceeding 
the primer consensus cut-off.

## Reads per UMI

```{r, echo=FALSE, warning=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=plot_titles, 
                   style="size", sizing="figure")
```

`r figures("cons_size")`

## UMI read group primer frequencies

```{r, echo=FALSE, warning=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=plot_titles, 
                   style="prfreq", sizing="figure")
```

`r figures("cons_prfreq")`

```{r, echo=FALSE, warning=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=plot_titles, 
                   style="prsize", sizing="figure")
```

`r figures("cons_prsize")`

## UMI read group error rates

```{r, echo=FALSE, warning=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=plot_titles, 
                   style="error", sizing="figure")
```

`r figures("cons_error")`

```{r, echo=FALSE, warning=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=plot_titles, 
                   style="prerror", sizing="figure")
```

`r figures("cons_prerror")`
