---
output:
  pdf_document: default
  html_document: default
params:
    data: "."
    primers_1: "primers-1_table.tab"
    primers_2: "primers-2_table.tab"
    primer_titles: ["Read 1", "Read 2"]
---

```{r, message=FALSE, echo=FALSE, results="hide"}
# Setup
library(prestor)
library(knitr)
library(captioner)

# Titles
plot_titles <- params$primer_titles

# Captions
if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("primers_count", 
        paste("Count of assigned primers for",  plot_titles[1], "(top) and", plot_titles[2], "(bottom).",
              "The bar height indicates the total reads assigned to the given primer,
               stacked for those under the error rate threshold (Pass) and
               over the threshold (Fail)."))
figures("primers_hist", 
        paste("Distribution of primer match error rates for", plot_titles[1], "(top) and", plot_titles[2], "(bottom).",
              "The error rate is the percentage of mismatches between the primer sequence and the 
               read for the best matching primer. The dotted line indicates the error threshold used."))
figures("primers_error", 
        paste("Distribution of primer match error rates for", plot_titles[1], "(top) and", plot_titles[2], "(bottom),",
              "broken down by assigned primer. The error rate is the percentage of mismatches between the 
               primer sequence and the read for the best matching primer. The dotted line indicates the error
               threshold used."))
```

```{r, echo=FALSE}
primer_log_1 <- loadLogTable(file.path(params$data, params$primers_1))
primer_log_2 <- loadLogTable(file.path(params$data, params$primers_2))
```

# Primer Identification

The MaskPrimers tool supports identification of multiplexed primers and UMIs.
Identified primer regions may be masked (with Ns) or cut to mitigate downstream
SHM analysis artifacts due to errors in the primer region. An annotion is added to 
each sequences that indicates the UMI and best matching primer. In the case of
the constant region primer, the primer annotation may also be used for isotype 
assignment.

## Count of primer matches

```{r, echo=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=plot_titles,
                style="count", sizing="figure")
```

`r figures("primers_count")`

## Primer match error rates

```{r, echo=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=plot_titles, 
                style="hist", sizing="figure")
```

`r figures("primers_hist")`

```{r, echo=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=plot_titles, 
                style="error", sizing="figure")
```

`r figures("primers_error")`
