---
output:
  pdf_document: default
  html_document: default
params:
    data: "."
    primers_r1: "PrimerLogR1_table.tab"
    primers_r2: "PrimerLogR2_table.tab"
---

```{r, message=FALSE, echo=FALSE, results="hide"}
# Setup
library(prestor)
library(knitr)
library(captioner)
if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("primers_count", "Count of assigned primers for read 1 (top) and 
                          read 2 (bottom). The bar height indicates the
                          total reads assigned to the given primer, stacked
                          for those under the error rate threshold (Pass) and
                          over the threshold (Fail).")
figures("primers_hist", "Distribution of primer match error rates for 
                         read 1 (top) and read 2 (bottom). The error rate
                         is the percentage of mismatches between the 
                         primer sequence and the read for the best 
                         matching primer. The dotted line indicates the error
                         threshold used.")
figures("primers_error", "Distribution of primer match error rates for 
                          read 1 (top) and read 2 (bottom), broken down 
                          by assigned primer. The error rate
                          is the percentage of mismatches between the 
                          primer sequence and the read for the best 
                          matching primer. The dotted line indicates the error
                          threshold used.")
```

```{r, echo=FALSE}
primer_log_1 <- loadLogTable(file.path(params$data, params$primers_r1))
primer_log_2 <- loadLogTable(file.path(params$data, params$primers_r2))
```

# Primer Identification

The MaskPrimers tool supports identification of multiplexed primers and UMIs.
Identified primer regions may be masked (with Ns) or cut to mitigate downstream
SHM analysis artifacts due to errors in the primer region. An annotion is added to 
each sequences that indicates the UMI and best matching primer. In the case of
the constant region primer, the primer annotation may also be used for isotype 
assignment.

## Count of primer matches

```{r, echo=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=c("Read 1", "Read 2"),
              style="count", sizing="figure")
```

`r figures("primers_count")`

## Primer match error rates

```{r, echo=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=c("Read 1", "Read 2"), 
                style="hist", sizing="figure")
```

`r figures("primers_hist")`

```{r, echo=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=c("Read 1", "Read 2"), 
                style="error", sizing="figure")
```

`r figures("primers_error")`
