---
output:
  pdf_document: default
  html_document: default
params:
    data: "."
    quality_r1: "QualityLogR1_table.tab"
    quality_r2: "QualityLogR2_table.tab"
---

```{R, message=FALSE, echo=FALSE, results="hide"}
# Setup
library(prestor)
library(knitr)
library(captioner)
if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("quality", "Mean Phred quality scores for read 1 (top) and read 2 (bottom).")
```

```{r, echo=FALSE}
quality_log_1 <- loadLogTable(file.path(params$data, params$quality_r1))
quality_log_2 <- loadLogTable(file.path(params$data, params$quality_r2))
```

# Quality Scores

Quality filtering is an essential step in most sequencing workflows. pRESTO’s
FilterSeq tool remove reads with low mean Phred quality scores. 
Phred quality scores are assigned to each nucleotide base call in automated 
sequencer traces. The quality score (`Q`) of a base call is logarithmically 
related to the probability that a base call is incorrect (`P`):

$Q = -10 log_{10} P$

For example, a base call with `Q=30` is incorrectly assigned 1 in 1000 times. 
The most commonly used approach is to remove read with average `Q` below 20.


```{r, echo=FALSE}
plotFilterSeq(quality_log_1, quality_log_2, titles=c("Read 1", "Read 2"), sizing="figure")
```

`r figures("quality")`