---
output:
  pdf_document: default
  html_document: default
params:
    data: "."
    consensus_r1: "ConsensusLogR1_table.tab"
    consensus_r2: "ConsensusLogR2_table.tab"
---

```{R, message=FALSE, echo=FALSE, results="hide"}
# Setup
library(prestor)
library(knitr)
library(captioner)
if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("cons_size", "Histogram of UMI read group sizes (reads per UMI) for read 1 (top) and
                      read 2 (bottom). The x-axis indicates the number of reads 
                      in a UMI group and the y-axis is the number of UMI groups 
                      with that size. The Consensus and Total bars are overlayed
                      (not stacked) histograms indicating whether the distribution
                      has been calculated using the total number of reads (Total)
                      or only those reads used for consensus generation (Consensus).")
figures("cons_prfreq", "Histograms shoing the distribution of majority primer frequency 
                        for all UMI read groups for read 1 (top) and read 2 (bottom).")
figures("cons_prsize", "Violin plots showing the distribution of UMI read group sizes by 
                        majority primer for read 1 (top) and read 2 (bottom). 
                        Only groups with majority primer frequency 
                        over the PRFREQ threshold set when running BuildConsensus. 
                        Meaning, only retained UMI groups.")
figures("cons_error", "Histogram showing the distribution of UMI read group error rates for
                       read 1 (top) and read 2 (bottom).")
figures("cons_prerror", "Violin plots showing the distribution of UMI read group error rates by 
                        majority primer for read 1 (top) and read 2 (bottom). 
                        Only groups with majority primer frequency 
                        over the PRFREQ threshold set when running BuildConsensus. 
                        Meaning, only retained UMI groups.")
```

```{r, echo=FALSE}
consensus_log_1 <- loadLogTable(file.path(params$data, params$consensus_r1))
consensus_log_2 <- loadLogTable(file.path(params$data, params$consensus_r2))
```

# Generation of UMI Consensus Sequences

Reads sharing the same UMI are collapsed into a single consensus sequence by
the BuildConsensus tool. BuildConsensus considers several factors in determining
the final consensus sequence, including the number of reads in a UMI group, 
Phred quality scores (`Q`), primer annotations, and the number of mismatches 
within a UMI group. Quality scores are used to resolve conflicting base calls in
a UMI read group and the final consensus sequence is assigned consensus quality 
scores derived from the individual base quality scores. The numbers of reads in a UMI
group, number of matching primer annotations, and error rate (average base mismatches from 
consensus) are used as strict cut-offs for exclusion of erroneous UMI read groups.
Additionally, individual reads are excluded whose primer annotation differs from 
the majority in cases where there are sufficient number of reads exceeding 
the primer consensus cut-off.

## Reads per UMI

```{r, echo=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=c("Read 1", "Read 2"), 
                   style="size", sizing="figure")
```

`r figures("cons_size")`

## UMI read group primer frequencies

```{r, echo=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=c("Read 1", "Read 2"), 
                   style="prfreq", sizing="figure")
```

`r figures("cons_prfreq")`

```{r, echo=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=c("Read 1", "Read 2"), 
                   style="prsize", sizing="figure")
```

`r figures("cons_prsize")`

## UMI read group error rates

```{r, echo=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=c("Read 1", "Read 2"), 
                   style="error", sizing="figure")
```

`r figures("cons_error")`

```{r, echo=FALSE}
plotBuildConsensus(consensus_log_1, consensus_log_2, titles=c("Read 1", "Read 2"), 
                   style="prerror", sizing="figure")
```

`r figures("cons_prerror")`



